Review stages

### 2024-05-13 doc/review-stages.qmd
feat: add function to get abstracts

```{r}
#| tbl-cap: "Article titles we agreed to keep from the disagreement list."
targets::tar_read(titles_resolved_path) |>
  select("Article title" = title) |>
  knitr::kable()
```

@@

>>>>

```{r}
#| message: false
#| tbl-cap: "Article titles we agreed to keep from the disagreement list."
targets::tar_read(titles_resolved_path) |>
  read_csv() |>
  select("Article title" = title) |>
  knitr::kable()
```

The final list of titles we selected, between the agreed on ones as well
as the resolved ones, are:

```{r}
#| message: false
#| tbl-cap: "Article titles we reviewed and selected to continue for abstract review."
targets::tar_read(titles_selected) |>
  select("Article title" = title) |>
  knitr::kable()
```

@@

```{r}
targets::tar_read(titles_selected) |> 
  dplyr::pull(id) |> 
  openalex_retrieve_abstracts() |>
  jsonlite::toJSON() |> 
  jsonlite::parse_json() |>
  yaml::as.yaml() |>
  yaml::write_yaml(here("data/review/abstracts.yaml"))
```
